### 2017-08-24 paper/CoverLetter.tex
Updated cover letter

Hence there exist a multitude of ways to define a multidimensional space, a metric measuring a specific aspect thereof and a test for many hypothesis.
In theory this vast tool-kit should allow evolutionary biologists and ecologists to do many things.
There are numerous implementation of such analysis pipeline in numerous R packages (e.g. \texttt{Claddis}, \texttt{geomorph}, \texttt{ade4}, \texttt{vegan}, etc.) or even in other languages (e.g. \texttt{GINGKO} in javascript).
However, each of these implementations are particular to the software/package author's definition of the multidimensional space, metric and test.
This leads researchers to often use these tool-kits by default hampering them to use the best definitions of the space/metric/test fitted to their particular question.
At worst this leads in turn to wrong statistic claims, and, at best to time consuming code retro-engineering.

In this application manuscript entitled ``dispRity: an R package for measuring disparity'', I present a complete and flexible R package allowing to run multidimensional analysis where each parameter (the space, the metric and the test) can be easily defined by the user.
In fact, this package provides a tidy and modular environment where users can use their own multidimensional space defined as a matrix and apply to it any metric and any test (provided as functions).
This allows for highly modular multidimensional analysis and the tidy interface allows easily reproducible analysis.

>>>>

There exist a multitude of ways to define a multidimensional space, a metric measuring a specific aspect thereof and a test for many hypothesis.
There are numerous implementation of such analysis pipeline in several R packages (e.g. \texttt{Claddis}, \texttt{geomorph}, \texttt{ade4}, \texttt{vegan}, etc.) or even in other languages (e.g. \texttt{GINGKO} in javascript).
However, each of these implementations are particular to the software/package author's definition of the multidimensional space, metric and test.
This leads researchers to often use these tool-kits by default, thus hampering them to use the best definitions of the space/metric/test fitted to their particular question.
At worst this leads to wrong statistic claims, and, at best to time consuming code retro-engineering.

In this application manuscript entitled ``dispRity: an R package for measuring disparity'', I present a complete and flexible R package allowing to run multidimensional analysis where each parameter can be easily defined by the user (the space, the metric and the test).
In fact, this package provides a tidy and modular environment where users can use their own multidimensional space defined as a matrix and apply to it any metric and any test (provided as functions).
This allows for highly modular multidimensional analysis and the tidy interface allows easily reproducible analysis.
Finally, this package comes with an in depth gitbook manual covering most functionalities and being updated regularly following users requests.
